Homework 6

### 2019-11-12 hw6/MSimonsHW6.tex
Fixed hw6 problem 1

\item To prove that "is an associate of" is an equivalence relation on $R$, we
must show that it is reflexive, symmetric, and transitive.
\\
\\
First, since $R$ is a commutative ring, there exists some identity element in
$R$, $1_R$, such that $a1_R = a$.  We can say that $1_R$ is a unit since
$(1_{R})  (1_{R}) = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
and "is an associate of" is reflexive.
\\
\\
Next, let $a$, $b \in R$ such that $a$ is an associate of $b$.  Therefore,
there exist some unit, $u$, in $R$ such that $au = b$.  Since $u$ is a unit,
there also exists some unit $v \in R$ such that $uv = 1_R$.
\\
\\
If $a = bu$, then
\[
av = (bu)v
\] \[
av = buv
\] \[
av = b(uv)
\] \[
av = b1_{R}
\] \[
av = b
\]
Therefore, $b$ is an associate of $a$ and "is an associate of" is reflexive.
\\
\\
Finally, let $a$ be an associate of $b$ and let $b$ be an associate of $c$ for
some elements $a$, $b$, $c \in R$.  Therefore, $a = bu$ and $b = cv$ for some
units $u$, $v \in R$.
\\
\\
We notice that
\[
a = bu
\] \[
a = (cv)u
\] \[
a = c(vu)
\]
We know that $vu$ is a unit because there exists some
$v^{-1}$, $u^{-1} \in R$ such that $vv^{-1} = 1_R$ and $uu^{-1} = 1_R$ since
$v$ and $u$ are units.  Thus, $(vu)(v^{-1}u^{-1}) = (vv^{-1})(uu^{-1}) = 1_R$
and so $vu$ is a unit.  Since $vu$ is a unit, $a$ is an associate of $c$ and
"is an associate of" is transitive.

>>>>

\item To prove that ``is an associate of'' is an equivalence relation on $R$, we
must show that it is reflexive, symmetric, and transitive.
\\
\\
First, since $R$ is a commutative ring, there exists some identity element in
$R$, $1_R$, such that $a1_R = a$.  We can say that $1_R$ is a unit since
$(1_{R})  (1_{R}) = 1_{R}$.  Since $a1_R = a$, $a$ is an associate of $a$
and ``is an associate of'' is reflexive.
\\
\\
Next, let $a$, $b \in R$ such that $a$ is an associate of $b$.  Therefore,
there exist some unit, $u$, in $R$ such that $a = bu$.  Since $u$ is a unit,
there also exists some unit $v \in R$ such that $uv = 1_R$.
\\
\\
If $a = bu$, then
\[
av = buv = b1_{R} = b
\]
Therefore, $b$ is an associate of $a$ and ``is an associate of'' is reflexive.
\\
\\
Finally, let $a$ be an associate of $b$ and let $b$ be an associate of $c$ for
some elements $a$, $b$, $c \in R$.  Therefore, $a = bu$ and $b = cv$ for some
units $u$, $v \in R$.
\\
\\
We notice that
\[
a = bu = cvu
\]
We know that $vu$ is a unit because there exists some
$v^{-1}$, $u^{-1} \in R$ such that $vv^{-1} = 1_R$ and $uu^{-1} = 1_R$ since
$v$ and $u$ are units.  Thus, $(vu)(v^{-1}u^{-1}) = (vv^{-1})(uu^{-1}) = 1_R$
and so $vu$ is a unit.  Since $vu$ is a unit, $a$ is an associate of $c$ and
``is an associate of'' is transitive.
